```{}
```

---
title: "Final Project"
author: Tanner Smalling
formatt: html
execute: 
  echo: false
---

```{r}
#| label: herehere
#| fig-cap: "Loading code & Library"
#| echo: false
#| error: false
library(tidyverse)
library(gtsummary)
library(here)
pride <- read.csv(here::here("data", "pride_index.csv"))
```

@herehere is using campus pride data taken from <https://github.com/rfordatascience/tidytuesday#datasets> Campus Pride Index.

There are approximately `r nrow(pride)` universities in this data-set.

```{r}
#| label: tbl_summary
#| fig-cap: "Descriptive Statistics"
tbl_summary(
	pride,
	by = campus_name,
	include = c(campus_name, students, rating),
	label = list(
		campus_name = "University", 
		students = "Student Population",
		rating = "Rating"
	))
```

Here are some summary statistics looking at University, population, and their rating. The mean rating is `r mean(pride$rating)` and median is `r median(pride$rating)`

```{r}
#| label: Regressions
#| fig-cap: "Regression comparing population and school rating"
regression <-  lm(students ~ rating, data = pride)
tbl_regression(
	regression,
	intercept = TRUE
)
```

@Regressions is the regressions being run on @tbl_summary

```{r}
#| label: Histogram
#| fig-cap: "Histogram looking at frequency of student population"
hist(pride$students)
```

Our @Histogram is covering the frequency of student populations.
